\documentclass[11pt, a4paper]{letter}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[scale=0.85]{geometry}
\usepackage{parskip}
\usepackage{setspace}


\newcommand{\email}{jobs@rubenlopes.uk}
\newcommand{\fullName}{Ruben Lopes}

\setlength{\topmargin}{0pt}
\setlength{\headheight}{0pt}
\setlength{\headsep}{0pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}
\setlength{\textwidth}{6.5in}
\setlength{\oddsidemargin}{0pt}
\setlength{\evensidemargin}{0pt}

\signature{\fullName}
\address{}
\date{\today}

\begin{document}
\begin{letter}{Dear Hiring Manager,}

\opening{}
\onehalfspacing

I'm writing to express my interest in the \textbf{\jobPosition} position at \textbf{\recipientCompany}.
As a multi cloud engineer at Barclays and a recent Computer Science graduate from the University of Reading, I bring a strong foundation in software development, cloud technologies, and DevOps practices.

At my current role at Barclays, I work on developing and maintaining cloud infrastructure and services across AWS, Azure, and GCP. The main focus of my role is building and maintaining internal tools that interact with firewalls, proxies, and other enterprise systems using Python (FastAPI), PostgreSQL, and HTMX. I also manage CI/CD pipelines using Jenkins and GitLab CI. Securing applications and infrastructure is a top priority, and I have hands-on experience implementing security best practices in cloud environments.

My industrial placement at HP as a DevOps Engineer gave me practical experience building an internal monitoring application using Django that transformed how developers track and audit build changes. Working with Python, TypeScript, and Bash, I implemented automation pipelines using Jenkins, GitLab, and Docker. This role strengthened my understanding of modern development practices, particularly CI/CD pipelines, containerisation, and version control with Git.

At the Science and Technology Facilities Council, I had the opportunity to work on SasView, a scientific tool for small angle scattering analysis. I enhanced key features by optimising real space distance calculations and reducing detector data noise using techniques like Singular Value Decomposition. Working with Python, C, SciPy, and NumPy gave me valuable experience in software optimisation and data processing.

My passion for DevOps extends beyond work hours – I've built a home lab environment where I explore Infrastructure as Code, containerisation, and cloud platforms including AWS and Kubernetes. This personal project has allowed me to gain practical experience with automation, container optimisation, and application security.

Collaboration has been key throughout my internships and academic projects, where I've worked effectively with diverse teams. I stay current with software development methodologies like Agile and am proficient in JavaScript, Python, and C. I'm also expanding my skills in TypeScript and GoLang to broaden my technical capabilities.

I would welcome the chance to discuss how my technical background and problem-solving approach align with \textbf{\recipientCompany}'s needs. You can reach me at \phoneNumber{} or \email.

\closing{Best regards,}

\end{letter}
\end{document}
