\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem} % For custom itemise settings
\setlength{\parskip}{0pt} % Remove extra space between paragraphs
\setlength{\parindent}{0pt} % No paragraph indent
\usepackage{titlesec} % Custom section title spacing

% Reduce spacing above and below sections
\titlespacing*{\section}{0pt}{1ex}{1ex}
\titlespacing*{\subsection}{0pt}{1ex}{1ex}

\begin{document}

\begin{center}
    	\textbf{Ruben Joseph Lopes} \\
    	\textbf{Phone:} +44 0000 00000 \\
    	\textbf{Email:} \href{mailto:jobs@rubenlopes.uk}{jobs@rubenlopes.uk} \\
    	\textbf{LinkedIn:} \href{https://linkedin.com/in/ru4en}{linkedin.com/in/ru4en} \\
    	\textbf{GitHub:} \href{https://github.com/ru4en}{github.com/ru4en} \\
    	\textbf{Portfolio:} \href{http://www.rubenlopes.uk}{www.rubenlopes.uk} \\
\end{center}
\vspace{0.3cm}
\section*{Experience}

\textbf{Barclays} \\
\textit{Multi-Cloud Engineer (Graduate)} \hfill August 2025 – Present \\
Currently, I am part of the Multi-Cloud Engineering team at Barclays, where I am involved in developing and maintaining cloud infrastructure and services. Besides cloud technologies, I also work on full stack internal tools primarily using Python (FastAPI), PostgreSQL, and HTMX. Besides this I also work on CI/CD pipelines using Jenkins and automation using Bash and Ansible. This role not only enhances my technical skills but also provides me with a comprehensive understanding of the financial sector.


\begin{itemize}[left=5pt,labelsep=2pt,noitemsep]
    \item Experience with cloud platforms such as AWS, Azure, and GCP.
    \item Full stack development using Python (FastAPI), PostgreSQL, and HTMX.
    \item CI/CD pipelines using Jenkins and automation using Bash and Ansible.
\end{itemize}

\vspace{0.3cm}

\textbf{Reading Student Unions} \\
\textit{Website Developer} \hfill September 2024 – August 2025 \\
As a website developer I was responsible for front-end development and UI/UX enhancements of our Reading Students’ Union website, implementing responsive design and creating a custom UI library aligned with the brand. Beyond routine management, I overhauled legacy sections of the codebase to implement a more modular architecture, improving maintainability and site performance.

\begin{itemize}[left=5pt,labelsep=2pt,noitemsep]
    \item Developed and documented a custom Bootstrap based UI extension alongside a modular Service Layer, significantly reducing front-end development time and technical toil for new features.
    \item Utilised Python for data attribution and analysis, providing actionable insights into user engagement and site traffic.
    \item Aided in the implementation of Cloudflare security protocols, specifically configuring bot protection and web application firewall (WAF) rules to protect against brute force attacks and prevent false data entry.
\end{itemize}

\textbf{HP Inc. - Wolf Security} \\
\textit{DevOps Engineer (Industrial Placement)} \hfill July 2023 – June 2024 \\
In my role as a DevOps Engineer during my industrial placement at HP, I actively utilised React (Typescript) to make UI, used Python with Django to create REST APIs, contributed to the development of internal tools, and scripted in Bash and PowerShell. I was responsible for setting up services for production within virtual environments and gained hands-on experience with cloud technologies like Docker and virtualisation. Additionally, I gained hands-on experience with the software development lifecycle by using tools such as Git and Jenkins for setting up CI/CD pipelines.

\begin{itemize}[left=5pt,labelsep=2pt,noitemsep]
    \item Full stack development using Python (Django), PostgreSQL, MySQL, and building UI components using React.js and TypeScript.
    \item Hands-on experience with Linux (Debian-based), scripting in Python, PowerShell, and Bash.
    \item Developed Jenkins CI/CD pipelines using Groovy, Docker, GitHub, and Git.
\end{itemize}

\vspace{0.3cm}

\textbf{University of Reading - IT} \\
\textit{AV (Audio Visual) Assistant} \hfill November 2022 - June 2023 \\
During my tenure as an AV Assistant at the University of Reading, I troubleshooted issues with Windows and audio-visual equipment. This experience enhanced both my technical skills and soft skills, particularly in effective communication and collaborative problem-solving.

\begin{itemize}[left=5pt,labelsep=2pt,noitemsep]
    \item Troubleshooting Windows systems and audio-visual equipment.
\end{itemize}

\vspace{0.3cm}

\textbf{UKRI - Science and Technology Facilities Council} \\
\textit{Computational Scientist (Summer Placement)} \hfill June 2022 - September 2022 \\
I worked on the Sasview project at STFC, automating and improving parts of the software, which allowed me to gain experience in C and Python. I collaborated with software engineers and scientists globally, improving my teamwork and communication skills. I implemented significant features such as UI tabs, batch calculating, 2D data slicing, and data noise reduction using SVD.

\begin{itemize}[left=5pt,labelsep=2pt,noitemsep]
    \item Real-life experience programming in C and Python.
    \item Use of automated testing and version control (Git).
    \item Enhanced skills in planning, presenting, and documentation.
\end{itemize}

\vspace{0.5cm}

\section*{Certifications}
\begin{itemize}[left=5pt,labelsep=2pt,noitemsep]
    \item AWS Certified Cloud Practitioner – Issued November 2025
\end{itemize}

\vspace{0.5cm}

\section*{Education}
\textbf{University of Reading } \\
\textit{Bachelor’s in Computer Science} \hfill September 2021 - July 2025 \\
\textit{Grade: First Class - 72\%}

\vspace{0.2cm}
Gained a strong foundation in computer science theory and practice, with extensive hands-on experience in full-stack development, data-driven systems, and cloud technologies. Completed a variety of projects, including a Final Year Project (Grade: 71), and developed skills in AI, machine learning, compilers, networking, image analysis, NLP, and both Java and Python development. Many projects are available on GitHub.

My final year project involved researching and developing a LLM router library in Python, which optimises the use of large language models by routing requests to the most suitable model based on the query. The project is available on GitHub: (\href{https://github.com/ru4en/fyp-llm-routers}{llm-routers}). 

\begin{itemize}[left=5pt,labelsep=2pt,noitemsep]
    \item Developed a LLM router library in Python to optimise the use of large language models.
    \item Gained experience with AI and machine learning concepts.
    \item Programming in Python, Java, C, and JavaScript.
    \item Full stack web development using React.js, HTML, CSS, SQL, and JavaScript.
\end{itemize}

\vspace{0.3cm}

\textbf{New College Swindon} \\
\textit{GCSEs and BTEC Computing} \hfill September 2017 - June 2021 \\
GCSE (Maths, English, Physics, Chemistry and Biology) – Grades 4 - 6 \\
BTEC Level 3 In Computing – Distinction Star, Distinction, Distinction (D*DD) \\
During my BTEC award in Computing, I undertook coursework which helped me enhance my writing, coding, and design abilities. My lecturers emphasised best practices, which improved the quality of my work.

\begin{itemize}[left=5pt,labelsep=2pt,noitemsep]
    \item Using Databases and SQL Queries.
    \item The significance of cyber safety and security.
    \item Understanding of the Software Development Life Cycle.
\end{itemize}

\vspace{0.5cm}

\section*{Key Skills}
\begin{itemize}[left=5pt,labelsep=2pt,noitemsep]
    \item Proficiency in GNU/Linux, Windows Server.
    \item Experience with cloud platforms such as AWS, Azure, and GCP.
    \item Experience with CI/CD tools such as Jenkins and GitHub Actions.
    \item Experience with configuration management tools such as Ansible and Terraform.
    \item Full stack web development using React.js, HTML, CSS, SQL, and JavaScript.
    \item Programming in Java, C, C++, Go, and Python.
    \item Mathematical aptitude and problem-solving skills.
    \item Knowledge of virtualisation (Oracle Virtual Box, QEMU) and containerisation (Docker).
    \item Shell scripting in Bash, Python, PowerShell.
    \item Writing tests using Playwright and PyTest.
\end{itemize}

\vspace{0.5cm}

\textbf{References available on request.}

\end{document}
